Which of my Transient Type Checks are not (Almost) Free?

### 2019-09-10 paper.tex
Update CCS and keywords

\documentclass[sigplan,10pt,screen]{acmart}\settopmatter{printfolios=true}

@@

%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011041.10011044</concept_id>
<concept_desc>Software and its engineering~Just-in-time compilers</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011008.10011009.10011011</concept_id>
<concept_desc>Software and its engineering~Object oriented languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011041.10010943</concept_id>
<concept_desc>Software and its engineering~Interpreters</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Just-in-time compilers}
\ccsdesc[300]{Software and its engineering~Object oriented languages}
\ccsdesc[300]{Software and its engineering~Interpreters}

\keywords{dynamic type checking, gradual types, optional types, Grace,
object-oriented programming}
\maketitle

@@

\bibliography{references}

\end{document}

>>>>

\documentclass[sigplan,screen]{acmart}

@@

%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\ccsdesc[500]{Software and its engineering~Software performance}
\ccsdesc[300]{Software and its engineering~Object oriented languages}
\ccsdesc[300]{Software and its engineering~Just-in-time compilers}

\keywords{dynamic type checking, gradual types, optional types, Grace,
performance evaluation, benchmarking, object-oriented programming}
\maketitle

@@

\bibliography{references}
\end{document}
